---
title: "Sebastián Ayala-Ruano CV"
author: Sebastián Ayala-Ruano
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
  cache_data:
    value: true
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r 'setup', include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

# Import libraries
library(glue)
library(tidyverse)
library(magrittr) # For the pipe
# Source the function to print contents from the googlesheet into the html or pdf
source("CV_printing_functions.R")

# Variables with urls of the pdf and html
CV_PDF_LOC <- "http://sayalaruano.github.io/cv/sayalaruano_cv.pdf"
CV_HTML_LOC <- "[sayalaruano.github.io/cv](http://sayalaruano.github.io/cv)"

# Create CV variable, obtained from the cache of the render function
CV <- readr::read_rds('cached_positions.rds')
```

```{css, echo=FALSE}
/* This chunk removes the side bar of all of the pages except the first one*/
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```

Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```

<p align="center">
    <a href="https://www.twitter.com/sayalaruano/" target="blank"><img align="center"  src="./css/icons/twitter.svg" alt="Twitter" height="20" width="20"/></a>
    <a href="https://github.com/sayalaruano" target="blank"><img align="center"  src="./css/icons/github.svg" alt="GitHub" height="20" width="20" /></a>
    <a href="https://www.linkedin.com/in/sayalaruano" target="blank"><img align="center" src="./css/icons/linkedin.svg" alt="LinkedIn" height="20" width="20" /></a>
    <a href="https://orcid.org/0000-0001-9756-6745" target="blank">
    <img align="center" src="./css/icons/orcid.svg" alt="orCID" height="20" width="20" /></a>
    <a href="https://www.researchgate.net/profile/Sebastian-Ayala-Ruano" target="blank">
    <img align="center" src="./css/icons/researchgate.svg" alt="Researchgate" height="20" width="20"/></a> 
</p>

Skills {#skills}
--------------------------------------------------------------------------------
<i class="fa fa-laptop"></i> **Technical**

Programming Languages:
<table>
    <td><img src="./css/icons/python-plain-wordmark.svg" alt="Python" width="30" height="30"/> </td>
    <td><img src="./css/icons/r-plain.svg" alt="R" width="30" height="30"/> </td>
    <td><img src="./css/icons/bash.svg" alt="bash" width="45" height="30"/> </td>
    <td><img src="./css/icons/cplusplus-plain.svg" alt="c++" width="30" height="30"/> </td>
    <td><img src="./css/icons/java-plain-wordmark.svg" alt="java" width="30" height="30"/></td>
</table>

<br>
DevOps:
<table>
     <td><img src="./css/icons/github-original-wordmark.svg" alt="github" width="30" height="30"/></td>
     <td><img src="./css/icons/git-original-wordmark.svg" alt="git" width="30" height="30"/></td>
     <td><img src="./css/icons/docker-plain-wordmark.svg" alt="Docker" width="30" height="30"/></td>
</table>

<br>
Data Science:
<table>
    <td><img src="./css/icons/jupyter-plain-wordmark.svg" alt="jupyter" width="30" height="30"/></td>
    <td><img src="./css/icons/python-plain-wordmark.svg" alt="Python" width="30" height="30"/> </td>
    <td><img src="./css/icons/r-plain.svg" alt="R" width="30" height="30"/> </td>
</table>

<br>
Databases and Cloud:
<table>
     <td><img src="./css/icons/mysql-plain-wordmark.svg" alt="mysql" width="30" height="30"/></td>
     <td><img src="./css/icons/postgresql-plain-wordmark.svg" alt="postgresql" width="30" height="30"/></td>
     <td><img src="./css/icons/firebase-plain-wordmark.svg" alt="firebase" width="45" height="30"/> </td>
     <td><img src="./css/icons/neo4j.svg" alt="neo4j" width="30" height="30"/> </td>
</table>
<br>

<i class="fa fa-language" aria-hidden="true"></i> **Languages**

- Spanish: Native

- English: Advanced | C1 | TOEFL iBT 109 

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

The source code is available at [sayalaruano/cv](https://github.com/sayalaruano/cv).

Last updated on `r Sys.Date()`.

```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(params$pdf_mode){
  glue("View this CV online at {CV_HTML_LOC}")
} else {
  glue("[<i class='fas fa-download'></i> Download a PDF of this CV]({CV_PDF_LOC})")
}
```

Main
================================================================================

Sebastián Ayala-Ruano {#title}
--------------------------------------------------------------------------------

```{r 'intro'}
CV %<>% print_text_block("intro")
```

Education {#education data-icon=graduation-cap} 
--------------------------------------------------------------------------------

```{r 'education'}
CV %<>% print_section('education')
```

Work Experience {#work data-icon=suitcase} 
--------------------------------------------------------------------------------

```{r 'work'}
CV %<>% print_section('work_positions')
```

Teaching Experience {#teaching data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r 'teaching'}
CV %<>% print_section('teaching_positions')
```

Publications {#pub data-icon=book}
--------------------------------------------------------------------------------

```{r 'pub'}
CV %<>% print_text_block("pub")
```

Selected presentations {#conf data-icon=chalkboard}
--------------------------------------------------------------------------------

```{r 'conf'}
CV %<>% print_text_block("conf")
```

Honors and Awards {#honors data-icon=medal}
--------------------------------------------------------------------------------

```{r 'honors'}
CV %<>% print_section("honors")
```


Leadership and Service {#leadership data-icon=users}
--------------------------------------------------------------------------------

```{r 'service'}
CV %<>% print_section("service")
```

{#others}
--------------------------------------------------------------------------------

```{r 'others'}
CV %<>% print_text_block("others")
```

